---
title: "ALL 52 counts lag7 stock values and skews each year 2007-2019"
author: "Janis Corona"
date: "3/9/2020"
output: html_document
---

This script combines the 52 stocks we have data on and the lag7 price value counts for decreasing and increasing cumulative sums and groups of counts with the number of times that group occurred in each of the years from 2007 and up to 2020.

```{r}
library(dplyr)

```



Read in the tables.
```{r}
ALL_52_2007_2020 <- read.csv('ALL_52_groups_skews.csv', sep=',', header=TRUE, 
                             na.strings=c('',' ','NA'))

ALL_52_2007_2020 <- ALL_52_2007_2020[,-c(7,8)]
colnames(ALL_52_2007_2020)[2:3] <- c('avgStockValue','medianStockValue')
a0 <- ALL_52_2007_2020
colnames(a0)[c(2:30)] <- paste(colnames(a0)[c(2:30)],'_Jan2007Feb2020',sep='')

ALL_52_2019 <- read.csv('ALL_52_groups_skews_2019.csv', sep=',', header=TRUE, 
                             na.strings=c('',' ','NA'),row.names=1)
a1 <- ALL_52_2019[,-c(2:3)]

ALL_52_2018 <- read.csv('ALL_52_groups_skews_2018.csv', sep=',', header=TRUE, 
                             na.strings=c('',' ','NA'),row.names=1)
a2 <- ALL_52_2018[,-c(2:3)]

ALL_52_2017 <- read.csv('ALL_52_groups_skews_2017.csv', sep=',', header=TRUE, 
                             na.strings=c('',' ','NA'),row.names=1)
a3 <- ALL_52_2017[,-c(2:3)]

ALL_52_2016 <- read.csv('ALL_52_groups_skews_2016.csv', sep=',', header=TRUE, 
                             na.strings=c('',' ','NA'),row.names=1)
a4 <- ALL_52_2016[,-c(2:3)]

ALL_52_2015 <- read.csv('ALL_52_groups_skews_2015.csv', sep=',', header=TRUE, 
                             na.strings=c('',' ','NA'),row.names=1)
a5 <- ALL_52_2015[,-c(2:3)]

ALL_52_2014 <- read.csv('ALL_52_groups_skews_2014.csv', sep=',', header=TRUE, 
                             na.strings=c('',' ','NA'),row.names=1)
a6 <- ALL_52_2014[,-c(2:3)]

ALL_52_2013 <- read.csv('ALL_52_groups_skews_2013.csv', sep=',', header=TRUE, 
                             na.strings=c('',' ','NA'),row.names=1)
a7 <- ALL_52_2013[,-c(2:3)]

ALL_52_2012 <- read.csv('ALL_52_groups_skews_2012.csv', sep=',', header=TRUE, 
                             na.strings=c('',' ','NA'),row.names=1)
a8 <- ALL_52_2012[,-c(2:3)]

ALL_52_2011 <- read.csv('ALL_52_groups_skews_2011.csv', sep=',', header=TRUE, 
                             na.strings=c('',' ','NA'),row.names=1)
a9 <- ALL_52_2011[,-c(2:3)]

ALL_52_2010 <- read.csv('ALL_52_groups_skews_2010.csv', sep=',', header=TRUE, 
                             na.strings=c('',' ','NA'),row.names=1)
a10 <- ALL_52_2010[,-c(2:3)]

ALL_52_2009 <- read.csv('ALL_52_groups_skews_2009.csv', sep=',', header=TRUE, 
                             na.strings=c('',' ','NA'),row.names=1)
a11 <- ALL_52_2009[,-c(2:3)]

ALL_52_2008 <- read.csv('ALL_52_groups_skews_2008.csv', sep=',', header=TRUE, 
                             na.strings=c('',' ','NA'),row.names=1)
a12 <- ALL_52_2008[,-c(2:3)]

ALL_52_2007 <- read.csv('ALL_52_groups_skews_2007.csv', sep=',', header=TRUE, 
                             na.strings=c('',' ','NA'),row.names=1)
a13 <- ALL_52_2007[,-c(2:3)]

ALL_52_2020 <- read.csv('ALL_52_groups_skews_2020.csv', sep=',', header=TRUE, 
                             na.strings=c('',' ','NA'),row.names=1)
a14 <- ALL_52_2020[,-c(2:3)]



```

Combine the table data.
```{r}
A1 <- merge(a0,a1, by.x='stockName', by.y='stock_2019')

A2 <- merge(A1,a2,by.x='stockName', by.y='stock_2018')

A3 <- merge(A2,a3,by.x='stockName', by.y='stock_2017')

A4 <- merge(A3,a4,by.x='stockName', by.y='stock_2016')

A5 <- merge(A4,a5,by.x='stockName', by.y='stock_2015')

A6 <- merge(A5,a6,by.x='stockName', by.y='stock_2014')

A7 <- merge(A6,a7,by.x='stockName', by.y='stock_2013')

A8 <- merge(A7,a8,by.x='stockName', by.y='stock_2012')

A9 <- merge(A8,a9,by.x='stockName', by.y='stock_2011')

A10 <- merge(A9,a10,by.x='stockName', by.y='stock_2010')

A11 <- merge(A10,a11,by.x='stockName', by.y='stock_2009')

A12 <- merge(A11,a12,by.x='stockName', by.y='stock_2008')

A13 <- merge(A12,a13,by.x='stockName', by.y='stock_2007')

A14 <- merge(A13,a14,by.x='stockName', by.y='stock_2020')

```

Rearrange the columns and add row names to the table of the stock names.
```{r}
A15 <- A14[,c(1,5,6,7,8,9,2:4,10:408)]
row.names(A14) <- A14$stockName

write.csv(A14, 'counts52stocksAndStats_fat.csv', row.names=TRUE)
```

This is great to look at as a long table of the useful data as meta data. The class type of each field will be factor for the 52 stocks.
```{r}
A15 <- as.data.frame(t(A14))
write.csv(A15,'counts52stocksAndStats_long.csv', row.names=TRUE)
```



***
***
***




We have our big data table of year and total ROI, cumulative counts, and number of times the groups of counts in total and for each year of each of these 52 stocks that had data from our hand picked stocks of 65 from Jan 3, 2007 to Feb 14 2020. Lets bring in some other tables and get month and quarter counts for each year.
```{r}
stocks <- read.csv('StocksAll07-20.csv', sep=',', header=TRUE, na.strings=c('',' '),
                   row.names=1)

```



```{r}
volume <- grep('Volume', colnames(stocks))
portfolio <- grep('portfolio', colnames(stocks))
stockValues <- stocks[,-c(15,volume, portfolio,107,116)]
colnames(stockValues) <- gsub('.Close','', colnames(stockValues))
colnames(stockValues)
```


```{r}
prices <- gather(stockValues, 'stockName', 'stockValue', 1:52)
colnames(prices)
row.names(prices) <- NULL
```


```{r}
Jan <- subset(prices, prices$Month=='Jan')
Feb <- subset(prices, prices$Month=='Feb')
Mar <- subset(prices, prices$Month=='Mar')
Apr <- subset(prices, prices$Month=='Apr')
May <- subset(prices, prices$Month=='May')
Jun <- subset(prices, prices$Month=='Jun')
Jul <- subset(prices, prices$Month=='Jul')
Aug <- subset(prices, prices$Month=='Aug')
Sep <- subset(prices, prices$Month=='Sep')
Oct <- subset(prices, prices$Month=='Oct')
Nov <- subset(prices, prices$Month=='Nov')
Dec <- subset(prices, prices$Month=='Dec')
```



Get the quantiles for 25th, 50th, 75th, and 100th stock values for each month from 2007-Feb 2020.
```{r}

jq25 <- Jan %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=.25))
jq50 <- Jan %>% group_by(stockName) %>% summarise(median(stockValue))
jq75 <- Jan %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=.75))
jq100 <- Jan %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=1))

fq25 <- Feb %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=.25))
fq50 <- Feb %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=.5))
fq75 <- Feb %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=.75))
fq100 <- Feb %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=1))

mrq25 <- Mar %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=.25))
mrq50 <- Mar %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=.5))
mrq75 <- Mar %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=.75))
mrq100 <- Mar %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=1))

apq25 <- Apr %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=.25))
apq50 <- Apr %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=.5))
apq75 <- Apr %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=.75))
apq100 <- Apr %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=1))

my25 <- May %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=.25))
my50 <- May %>% group_by(stockName) %>% summarise(median(stockValue))
my75 <- May %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=.75))
my100 <- May %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=1))

jn25 <- Jun %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=.25))
jn50 <- Jun %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=.5))
jn75 <- Jun %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=.75))
jn100 <- Jun %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=1))

jlq25 <- Jul %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=.25))
jlq50 <- Jul %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=.5))
jlq75 <- Jul %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=.75))
jlq100 <- Jul %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=1))

agq25 <- Aug %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=.25))
agq50 <- Aug %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=.5))
agq75 <- Aug %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=.75))
agq100 <- Aug %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=1))

sp25 <- Sep %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=.25))
sp50 <- Sep %>% group_by(stockName) %>% summarise(median(stockValue))
sp75 <- Sep %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=.75))
sp100 <- Sep %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=1))

oc25 <- Oct %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=.25))
oc50 <- Oct %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=.5))
oc75 <- Oct %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=.75))
oc100 <- Oct %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=1))

nvq25 <- Nov %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=.25))
nvq50 <- Nov %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=.5))
nvq75 <- Nov %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=.75))
nvq100 <- Nov %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=1))

dcq25 <- Dec %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=.25))
dcq50 <- Dec %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=.5))
dcq75 <- Dec %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=.75))
dcq100 <- Dec %>% group_by(stockName) %>% summarise(quantile(stockValue, probs=1))
```




```{r}

stockQuantiles <- cbind(jq50,jq75,jq100,
                        fq25,fq50,fq75,fq100,
                        mrq25,mrq50,mrq75,mrq100,
                        apq25,apq50,apq75,apq100,
                        my25,my50,my75,my100,
                        jn25,jn50,jn75,jn100,
                        jlq25,jlq50,jlq75,jlq100,
                        agq25,agq50,agq75,agq100,
                        sp25,sp50,sp75,sp100,
                        oc25,oc50,oc75,oc100,
                        nvq25,nvq50,nvq75,nvq100,
                        dcq25,dcq50,dcq75,dcq100)


stq <- grep('stockName', colnames(stockQuantiles))

stockQuantiles <- stockQuantiles[,-stq]

stockQuantiles <- cbind(jq25,stockQuantiles)


```



```{r}
names <- c('stockName',
           'Jan_Quantile1','Jan_Quantile2','Jan_Quantile3','Jan_Quantile4',
           'Feb_Quantile1','Feb_Quantile2','Feb_Quantile3','Feb_Quantile4',
           'Mar_Quantile1','Mar_Quantile2','Mar_Quantile3','Mar_Quantile4',
           'Apr_Quantile1','Apr_Quantile2','Apr_Quantile3','Apr_Quantile4',
           'May_Quantile1','May_Quantile2','May_Quantile3','May_Quantile4',
           'Jun_Quantile1','Jun_Quantile2','Jun_Quantile3','Jun_Quantile4',
           'Jul_Quantile1','Jul_Quantile2','Jul_Quantile3','Jul_Quantile4',
           'Aug_Quantile1','Aug_Quantile2','Aug_Quantile3','Aug_Quantile4',
           'Sep_Quantile1','Sep_Quantile2','Sep_Quantile3','Sep_Quantile4',
           'Oct_Quantile1','Oct_Quantile2','Oct_Quantile3','Oct_Quantile4',
           'Nov_Quantile1','Nov_Quantile2','Nov_Quantile3','Nov_Quantile4',
           'Dec_Quantile1','Dec_Quantile2','Dec_Quantile3','Dec_Quantile4')

colnames(stockQuantiles) <- names
head(stockQuantiles)
```



