---
title: "Quandmod-Quantitative Finance R tutorial Youtube"
author: "Janis Corona"
date: "1/20/2020"
output:
  word_document: default
  html_document:
    df_print: paged
  pdf_document: default
---

This is a youtube tutorial on quant finance from 'Quant Finance with R Part 1 intro and Data": [This tutorial link](https://www.youtube.com/watch?v=uwuPQUa2TjI).

The [github repository](https://github.com/fdupuis659/Quant-Finance-with-R) for these tutorials are at: https://github.com/fdupuis659/Quant-Finance-with-R



* $install.packages('quantmod')$ 
* $install.packages('PerformanceAnalytics)$

The above package, quantmod, is used for quantitative finance in R.
The PerformanceAnalytics package is used to analyze the data using quantmod in R.

```{r, error=FALSE, message=FALSE, warning=FALSE}
library(quantmod)
library(PerformanceAnalytics)
```


* $?quantmod$
* $?getSymbols$

***

This sets a minimum date to grab out of the AAPL finance data
so that all dates will be after Feb 1, 2017.
```{r, error=F, warning=F, message=F}

dt <- '2011-2-1'

aapl <- getSymbols.yahoo('AAPL', from = dt, auto.assign=F)
```
The above object is an 'xts' object or extensible time series object used in financial markets.


```{r}
head(aapl)
```

```{r}
dim(aapl)
row.names(aapl)[1:20]
colnames(aapl)
```


The following are also xts objects.
```{r}

aaplClose <- aapl[,6]


# use of the PerformanceAnalytics library loaded earlier
appleReturns <- dailyReturn(aaplClose, type='log')

appleReturns1 <- na.omit(dailyReturn(aaplClose, type='log'))
```

```{r}
head(appleReturns)
head(appleReturns1)

```

The NAs should have been removed but are being read in as zeros, from quantmod when getting the 'AAPL' xts object from the web.



The following will chart a graph of the xts object, aapl.
```{r, warning=F, message=F, erro=F}
chartSeries(aapl)
```




*** 

[Quant Finance with R Part 2: Portfolio Analysis](https://www.youtube.com/watch?v=2Y4HX0UUcrA): (https://www.youtube.com/watch?v=2Y4HX0UUcrA)  of 4 parts for this Quantitative Finance tutorial on Youtube from December 2018.
```{r, error=FALSE, message=FALSE, warning=FALSE}
library(quantmod)
library(PerformanceAnalytics)
```

Function that uses the closing price column to add the prices since a set date.
```{r, message=FALSE, error=FALSE, warning=FALSE}
tickers <- c('FB', 'AAPL','NFLX')

weights <- c(0.25, 0.25, 0.25)

portfolioPrices <- NULL

for (ticker in tickers){
  portfolioPrices <- cbind(portfolioPrices, getSymbols.yahoo(ticker,
  from = '2016-01-03', periodicity='daily', auto.assign=FALSE)[,4])
  
}
```

Check NAs not in data.
```{r}
colSums(is.na(portfolioPrices))
```

S&P benchmark
```{r, warning=FALSE, error=FALSE, message=FALSE}
benchmarkPrices <- getSymbols.yahoo('^GSPC', from='2016-01-03', periodicity='daily', auto.assign=FALSE)[,4]
```


Calculate daily change in each column.
```{r}
benchmarkReturns <- na.omit(ROC(benchmarkPrices))
colSums(is.na(benchmarkReturns))
```

```{r}
portfolioReturns <- na.omit(ROC(portfolioPrices))
colSums(is.na(portfolioReturns))
```


```{r}
portfolioReturn <- Return.portfolio(portfolioReturns)
```

To find out more on the Return.portfolio function, use:
* $?Return.portfolio$


***

***

Some side information about a few financial algorithms:

* __CAPM__: formula for expected return with calculated risk on an asset or stock.
* __ALPHA__: risk adjustment metric for performances compares to an index and shows how much better that index is beat by your benchmark.
* __BETA__: measure of volatility with <1 => less risky and >1 => more risky.
* __SHARPE RATIO__: risk metric for every standard deviation unit, how much return is achieved, gives risk & reward, and most widely used metric with finance managers.


The number of trading days is 252 days a year.
```{r}
CAPM.beta(portfolioReturn, benchmarkReturns, 0.035/252)

```

```{r}
CAPM.jensenAlpha(portfolioReturn, benchmarkReturns, 0.035/252)
```


```{r}
SharpeRatio(portfolioReturn, 0.035/252)
```

```{r}
table.AnnualizedReturns(portfolioReturn)
```

```{r}
table.CalendarReturns(portfolioReturn)
```

***

***
[Quant Finance Part 3: Portfolio Optimization](https://www.youtube.com/watch?v=6Pi0fjARtUI): https://www.youtube.com/watch?v=6Pi0fjARtUI 

Same libraries and code above used, but add in more tickers.
```{r, message=FALSE, error=FALSE, warning=FALSE}
tickers <- c('FB', 'AAPL','NFLX','AMZN','GOOGL','SQ','NVDA')

weights <- c(0.25, 0.25, 0.25)

portfolioPrices <- NULL

for (ticker in tickers){
  portfolioPrices <- cbind(portfolioPrices, getSymbols.yahoo(ticker,
  from = '2016-01-03', periodicity='daily', auto.assign=FALSE)[,4])
  
}
```


S&P benchmark
```{r, warning=FALSE, error=FALSE, message=FALSE}
benchmarkPrices <- getSymbols.yahoo('^GSPC', from='2011-01-01', periodicity='daily', auto.assign=FALSE)[,4]
```


Calculate daily change in each column.
```{r}
benchmarkReturns <- na.omit(ROC(benchmarkPrices))
portfolioReturns <- na.omit(ROC(portfolioPrices))
portfolioReturn <- Return.portfolio(portfolioReturns)

```

$install.packages('imputeTS')$
$install.packages('PortfolioAnalytics')$

```{r}
library(dplyr)
library(quantmod)
library(PerformanceAnalytics)
library(imputeTS)
library(PortfolioAnalytics)
```

```{r}
portf <- portfolio.spec(colnames(portfolioReturns))

portf <- add.constraint(portf, type="weight_sum", min_sum=1, max_sum=1)
portf <- add.constraint(portf, type="box", min=.10, max=.40)
portf <- add.objective(portf, type="return", name="mean")
portf <- add.objective(portf, type="risk", name="StdDev")


```

Need to install some more libraries to run the optimize.portfolio().

* $install.packages('ROI')$
* $install.packages('ROI.plugin.quadprog')$
* $install.packages('ROI.plugin.glpk')$

```{r}
library(ROI)
library(ROI.plugin.quadprog)
library(ROI.plugin.glpk)

```


```{r}
optPort <- optimize.portfolio(portfolioReturns, portf, optimize_method = "ROI", trace=TRUE)
```

```{r, fig.width=6, fig.height=6}
chart.Weights(optPort)
```

```{r}
ef <- extractEfficientFrontier(optPort, match.col = "StdDev", n.portfolios = 25,
                         risk_aversion = NULL)
```

```{r, fig.width=8, fig.height=8}
chart.EfficientFrontier(ef,
                        match.col = "StdDev", n.portfolios = 25, xlim = NULL, ylim = NULL,
                        cex.axis = 0.8, element.color = "darkgray", main = "Efficient Frontier",
                        RAR.text = "SR", rf = 0, tangent.line = TRUE, cex.legend = 0.8,
                        chart.assets = TRUE, labels.assets = TRUE, pch.assets = 21,
                        cex.assets = 0.8)
```


***

***

[Quant Finance Part 4: Portfolio Optimization Backtest](https://www.youtube.com/watch?v=mBjdkAVdhgM): https://www.youtube.com/watch?v=mBjdkAVdhgM

```{r, warning=FALSE, message=FALSE, error=FALSE}
library(quantmod)
library(PerformanceAnalytics)
library(PortfolioAnalytics)
```

```{r, warning=FALSE, error=FALSE, message=FALSE}
tickers <- c("FB", "AAPL", "AMZN", "NFLX", "GOOGL", "SQ", "NVDA")

portfolioPrices <- NULL
for(ticker in tickers) {
  portfolioPrices <- cbind(portfolioPrices,
                           getSymbols.yahoo(ticker, from='2016-01-03', periodicity = 'daily', auto.assign=FALSE)[,4])
}

portfolioReturns <- na.omit(ROC(portfolioPrices))

portf <- portfolio.spec(colnames(portfolioReturns))

portf <- add.constraint(portf, type="weight_sum", min_sum=0.99, max_sum=1.01)
portf <- add.constraint(portf, type="transaction_cost", ptc = 0.001)
portf <- add.constraint(portf, type="box", min=.10, max=.40)
portf <- add.objective(portf, type="return", name="mean")
portf <- add.objective(portf, type="risk", name="StdDev", target=0.005)
```

```{r}
rp <- random_portfolios(portf, 10000, "sample")
```

```{r, error=FALSE, message=FALSE, warning=FALSE}
opt_rebal <- optimize.portfolio.rebalancing(portfolioReturns,
                                           portf,
                                           optimize_method="random",
                                           rp=rp,
                                           rebalance_on="months",
                                           training_period=1,
                                           rolling_window=10)
```

```{r}
equal_weight <- rep(1 / ncol(portfolioReturns), ncol(portfolioReturns))
benchmark <- Return.portfolio(portfolioReturns, weights = equal_weight)
colnames(benchmark) <- "Benchmark Portfolio"
```

```{r, message=FALSE, error=FALSE, warning=FALSE}
sp500prices <- getSymbols.yahoo("SPY", from='2016-01-03', periodicity = 'daily', auto.assign=FALSE)[,4]
sp500Rets <- na.omit(ROC(sp500prices))
sp500Rets <- as.xts(sp500Rets)
```

```{r}
chart.Weights(opt_rebal, main="Rebalanced Weights Over Time")
```

```{r}
rebal_weights <-extractWeights(opt_rebal)
rebal_returns <- Return.portfolio(portfolioReturns, weights=rebal_weights)

rets_df <- cbind(rebal_returns, benchmark, sp500Rets)

charts.PerformanceSummary(rets_df, main="P/L Over Time")
```

