---
title: "ROI on Hand Picked Stocks 2007-2020"
author: "Janis Corona"
date: "2/17/2020"
output:
  word_document: default
  html_document: default
---

```{r, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}
library(lubridate)
library(tidyr)
```



```{r}
portfolio <- read.csv('all_portfolio_prices.csv', header=TRUE, na.strings=c('',' '),
                      row.names=1)
```


```{r}
portfolio$Date <- row.names(portfolio)
```

```{r}
Vol <- grep('Volume', colnames(portfolio))
close <- grep('Close',colnames(portfolio))
Close <- portfolio[,close]
Volume <- portfolio[,Vol]
colnames(Close)
```

Remove NAs from the data. The colSums(is.na(Close)) isn't returning the columns with NAs, so this must be done manually.
```{r}

Close_noNAs <- Close[,-c(9,13,17,18,25,27,32,34,46,50,61,65)]
Close_noNAs$SCE.PB.Close <- as.numeric(Close_noNAs$SCE.PB.Close)
```

Add in a value of the portfolio column for each day's closing price of all stock that don't have NAs.
```{r}
Close_noNAs$DailyValue <- rowSums(Close_noNAs,na.rm=TRUE)

```

Add in a daily change column of the portfolio closing prices.
```{r}
dayVal <- as.data.frame(Close_noNAs$DailyValue)
colnames(dayVal) <- 'previousDayValue'
zero <- as.data.frame(as.numeric(dayVal$previousDayValue[1]))
colnames(zero) <- 'previousDayValue'
prevDay <- rbind(zero,dayVal)
Close_noNAs$prevDay <- prevDay[1:3303,1]
dailyChange <- as.data.frame(Close_noNAs$DailyValue-Close_noNAs$prevDay)
colnames(dailyChange) <- 'dailyChange'

Close1 <- cbind(Close_noNAs,dailyChange)
```

Add a column that gives the return in dollars on initial dollars invested.
```{r}
Close1$ROI_dollars <- Close1$DailyValue-Close1$DailyValue[1]
```

Add some date fields to look at the values by date, day of the week, month, and year in analyzing this data.
```{r}
Close1$Date <- as.Date.character(row.names(Close1))
```

```{r}
Close1$DayOfWeek <- weekdays(as.Date(Close1$Date))
```

```{r}
month <- month(as.Date(Close1$Date))
Month <- month.abb[month]
Close1$Month <- Month
```


Add in the year of the Date column.
```{r}
Year <- year(as.Date(Close1$Date))

Close1$Year <- Year

Close1$MonthYear <- paste(Close1$Month, Close1$Year, sep='-')
Close1$MonthYear <- as.factor(Close1$MonthYear)
```



Add in some [unemployment](https://data.bls.gov/pdq/SurveyOutputServlet) information as a column to see how the portfolio is doing by date.
```{r}
ue <- read.delim('BLS_unemploymentRates2007-2020.txt', sep=',',header=TRUE, 
                 na.strings=c('',' '))
UE <- ue[,-14]#remove the empty 'Annual' column
```

Use tidyr to gather the month fields with their respective unemployment rates per month.
```{r}
gatherMonths <- gather(UE, 'UE_Month', 'UE_monthlyRate',2:13)

gatherMonths$MonthYear <- paste(gatherMonths$UE_Month, gatherMonths$Year, sep='-')
gatherMonths$MonthYear <- as.factor(gatherMonths$MonthYear)
```


```{r}
UE2 <- gatherMonths[,3:4]
Close2 <- merge(Close1, UE2, by.x='MonthYear', by.y='MonthYear')
```

```{r}
write.csv(Close2, 'ROI_UE_2007_2020.csv', row.names=FALSE)
```
