---
title: "Subset Large Stock Data Counts ROI Group Counts"
author: "Janis Corona"
date: "3/22/2020"
output:
  word_document: default
  html_document: default
---


%%%%%%%%%%%%%%%

This file relies on all others made, but can be ran using the kaggle large data set. To understand the file, it would be helpful to look at all files in the github folder. Both links are below.

***
***
***
```{r}
library(lubridate)
library(dplyr)
```

%%%%%%%%%%%%%%%

Retrieve the large (approximately 442 mb file size) from [Kaggle](https://www.kaggle.com/janiscorona/stock-day-counts-increasing-and-decreasing-0720) called allStocksGathered1.csv for the large data processed in the last part of this script and to get the individual stock stats and counts of increasing and decreasing days.This script is in [github](https://github.com/JanJanJan2018/Quantative-Finance) as newStocksLagsCountsGroups.Rmd that made the csv large data file just mentioned.
```{r}
allStocksGathered1 <- read.csv('allStocksGathered1.csv',sep=',', header=TRUE,
                               na.strings=c('',' ','NA'))
```

This data set is also needed and can be retrieved at the github link above.
```{r}
newStocks <- read.csv('StockSwingTradeBotCom.csv', header=TRUE, na.strings=c('',' ','NA'),
                      sep=',')

head(newStocks)

```

Lets create the lag and count/group by counts fields to analyze by each stock, using subsets of each stock.
```{r}
DF <- allStocksGathered1
DF$Date <- as.Date(DF$Date)
```

What stock ticker are you interested in? And what lag are you interested in? You can keep the lag from the top of this script or these defaults or change them here. You need to enter the stock name in the chunk for Rmarkdown below. Also, pick a start date and end date of the time you want to select for running the counts and groups of counts.
```{r}
stock_1 <- toupper("ubsi")
lag <- 3
startDate <- '2005-01-22'
endDate <- '2008-01-22'


```

Lets subset our large table to get the dates requested.
```{r}
sDF <- subset(DF, DF$Date>=startDate & DF$Date<=endDate)

```

```{r}
lagN <- paste('lag',lag,sep='')
cat('The number of days to retrieve the stock value compared to each day value listed as an instance is ',lag,'and the stock to look up this information for is ',stock_1)
stknme <- as.character(newStocks[newStocks$stockSymbol==stock_1,2])
cat('\nThis stock is ',stknme)

Lstock_1 <- subset(sDF, sDF$stockName==stock_1)

cat('The number of days for trading that this time period will provide counts of increasing and decreasing days is ', length(Lstock_1$Date), ' trading days.')

```


Generic automation of above stock to look up and the lag to use for generating the counts, group of counts, and lag values to get those counts.
```{r}
Lstock_1$startDayValue <-Lstock_1$stockValue[1]
Lstock_1$startDayDate <- Lstock_1$Date[1]
Lstock_1$finalDayValue <-Lstock_1$stockValue[length(Lstock_1$stockValue)]
Lstock_1$finalDayDate <- Lstock_1$Date[length(Lstock_1$Date)]

stock_1LN <- lag(Lstock_1$stockValue, lag)
Lstock_1$lagN <- stock_1LN
Lstock_1$today2_lagN <- Lstock_1$stockValue/Lstock_1$lagN
Lstock_1 <- Lstock_1[complete.cases(Lstock_1),]
```

Lets look at the data we will be adding counts of increasing and decreasing days, for the time interval dates and stock values at the beginning and end of the time interval available or requested.
```{r}
cat('\nThe lag for this table was for ',lag,'days.','\nThe stock to look up was ', stock_1,'.\nThe start date of this stock and starting value was ',as.character(paste(Lstock_1$startDayDate[1])),' and ','$',Lstock_1$startDayValue[1],'\nThe end date and end date price of this stock analysis is ',as.character(paste(Lstock_1$finalDayDate[1])),' and ','$',Lstock_1$finalDayValue[1])

roi <- Lstock_1$finalDayValue[1]/Lstock_1$startDayValue[1]
cat('\nThe return on investment as a percentage of the amount invested for this time period is ',roi)

cat('\n\nIn dollars initially invested your return  is $',Lstock_1$finalDayValue[1]-Lstock_1$startDayValue[1], 'for the dates:',
   as.character(paste(Lstock_1$startDayDate[1])),'through ',
   as.character(paste(Lstock_1$finalDayDate[1]))) 

```


Now, lets look at the counts and group counts of increasing and decreasing days for this stock and the time period available.
```{r}
#assign a 1 to increasing values
Lstock_1$todayGrtrThan_lagN <- ifelse(Lstock_1$today2_lagN>1, 1,0)

Lstock_1$cumulativeSumTodayGrtrThan_lagN <- cumsum(Lstock_1$todayGrtrThan_lagN)

# get the count of how many instances repeat, 
# those counts repeating are counts that measure the days cumulatively decreasing
# those cumulative counts that don't repeat, are counting increasing days.
# These are stock values for today's value to 7 days prior value.
countstock_10 <- Lstock_1 %>% group_by(cumulativeSumTodayGrtrThan_lagN) %>% count(n=n())
countstock_10 <- as.data.frame(countstock_10)
countstock_10 <- countstock_10[,-3]
colnames(countstock_10)[2] <- 'nRepeatsTodayGrtrThan_lagN'

# Count the REPEATS of each number (minus the initial start) 
countstock_10$decrDaysThisCycle <- countstock_10$n-1

# Count the number of times the cycle count repeats in this time span exactly that many days
countstock_10b <- countstock_10 %>% group_by(decrDaysThisCycle) %>% count(n=n())
countstock_10b <- as.data.frame(countstock_10b)
countstock_10b <- countstock_10b[,-3]
colnames(countstock_10b)[2] <- 'nTimesDecrDayCountsOccurs'

#combine these two count matrices of decreasing days
countsstock_tableDecr <- merge(countstock_10, countstock_10b, by.x='decrDaysThisCycle',
                             by.y='decrDaysThisCycle')

#combine the counts to the stock subset
stock_3 <- merge(Lstock_1, countsstock_tableDecr, by.x='cumulativeSumTodayGrtrThan_lagN',
               by.y='cumulativeSumTodayGrtrThan_lagN')

#assign a 1 to decreasing values
stock_3$todayLessThan_lagN <- ifelse(stock_3$today2_lagN>1, 0,1)

stock_3$cumulativeSumTodayLessThan_lagN <- cumsum(stock_3$todayLessThan_lagN)

# get the count of how many instances repeat, 
# those counts repeating are counts that measure the days cumulatively increasing
# those cumulative counts that don't repeat, are counting decreasing days.
# These are stock values for today's value to 7 days prior value.
countstock_11 <- stock_3 %>% group_by(cumulativeSumTodayLessThan_lagN) %>% count(n=n())
countstock_11 <- as.data.frame(countstock_11)
countstock_11 <- countstock_11[,-3]
colnames(countstock_11)[2] <- 'nRepeatsTodayLessThan_lagN'

# Count the REPEATS of each number (minus the initial start) 
countstock_11$incrDaysThisCycle <- countstock_11$n-1

# Count the number of times the cycle count repeats in this time span exactly that many days
countstock_11b <- countstock_11 %>% group_by(incrDaysThisCycle) %>% count(n=n())
countstock_11b <- as.data.frame(countstock_11b)
countstock_11b <- countstock_11b[,-3]
colnames(countstock_11b)[2] <- 'nTimesIncrDayCountsOccurs'

#combine these two count matrices of decreasing days
countsstock_tableIncr <- merge(countstock_11, countstock_11b,
                               by.x='incrDaysThisCycle',
                             by.y='incrDaysThisCycle')

#combine the counts to the stock subset
stock_4 <- merge(stock_3, countsstock_tableIncr,
                 by.x='cumulativeSumTodayLessThan_lagN',
               by.y='cumulativeSumTodayLessThan_lagN')
```

```{r}
colnames(stock_4)
```

```{r}
stock_5 <- stock_4[,c(3:11,
                      12,2,14,13,15,
                      16,1,18,17,19)]
colnames(stock_5) <- gsub('lagN',lagN,colnames(stock_5))
colnames(stock_5)
```


Using this information on one stock of the thousands available in our large csv file and table, lets return the count information and the number of times this stock has seen those exact days of counts.
```{r}
cat('\nThe number of times this stock has decreased in the current cycle from the start of this time period retrieved in price comparison of the number of days in lags retrieved prior to each instance dates\' stock value is ', stock_5$decrDaysThisCycle[length(stock_5$decrDaysThisCycle)],'\n')

cat('\nThe number of times this stock has increased in the current cycle from the start of this time period retrieved in price comparison of the number of days in lags retrieved prior to each instance dates\' stock value is ', stock_5$incrDaysThisCycle[length(stock_5$incrDaysThisCycle)],'\n')

cat('\nThe number of times this stock has decreased exactly this number of days compared to its price ', lag, ' days ago, is ', stock_5$nTimesDecrDayCountsOccurs[length(stock_5$nTimesDecrDayCountsOccurs)],'\n')

cat('\nThe number of times this stock has increased exactly this number of days compared to its price ', lag, ' days ago, is ', stock_5$nTimesIncrDayCountsOccurs[length(stock_5$nTimesIncrDayCountsOccurs)],'\n')


```

The unique number of days this stock selected (for the time period retrieved) decreased is shown in the table below.
```{r}
stock_5[unique(stock_5$decrDaysThisCycle),c(1:3,8,9,13,14)]
```

The unique number of days this stock selected (for the time period retrieved) increased is shown in the table below.
```{r}
stock_5[unique(stock_5$incrDaysThisCycle),c(1:3,8,9,18,19)]


```


%%%%%%%%%%%%%%%%%

***
***
***


